\documentclass[UTF8]{ctexart}
\usepackage{framed,xcolor}
\usepackage{amsmath,amssymb,varwidth,tikz}
\usetikzlibrary{calc}
 
%定义加框环境；==============================================================================================================================
\newcommand{\mybox}[4][\textwidth-\pgfkeysvalueof{/pgf/inner xsep}-2mm]{%
\begin{figure}[!ht]
    \centering
    \begin{tikzpicture}
        \node[line width=.5mm, rounded corners, draw=#2, inner ysep=10pt, text width=#1, outer sep=0] (one) 
        {\vspace*{15pt}\\\begin{varwidth}{\textwidth}#4\end{varwidth}};
        \node[text=white,anchor=north east,align=center, minimum height=20pt] (two) at (one.north east) {#3 \hspace*{.5mm}};
        \path[fill=#2] (one.north west|-two.west) -- ($(two.west)+(-1.5cm,0)$) to [out=0,in=180] (two.south west) --
        (two.south east) [rounded corners] --(one.north east) -- (one.north west) [sharp corners] -- cycle;
        \node[text=white,anchor=north east,align=center, minimum height=20pt, text height=2ex]
        (three) at (one.north east) {#3 \hspace*{.5mm}};
    \end{tikzpicture}
\end{figure}}
%================================================================================================================================定义加框环境；
%设置背景色
\definecolor{shadecolor}{cmyk}{1,0.5,0,0}
% \colorlet{shadecolor}{blue!20}
% 支持的字体 \songti、\heiti、\fangsong、\kaishu、\lishu、\youyuan

\begin{document}
    中文\LaTeX 示例。\\
    Cowards die many times before their deaths.\\
   { \kaishu 懦夫在未死之前，已身历多次死亡的恐怖了。（楷体）}

    \begin{verse}
        Stray birds of summer come to my window to sing and fly away. \\
        And yellow leaves of autumn, which have no songs, \\
        flutter and fall there with a sign.\\
        \hfill \emph{Rabindranath Tagore}
    \end{verse}
    \begin{verse}
       \heiti 夏天的飞鸟，飞到我的窗前唱歌，又飞去了。\\
        秋天的黄叶，它们没有什么可唱，只叹息一声，飞落在那里。（黑体）\\
        \hfill \emph{罗宾德拉纳特·泰戈尔}
    \end{verse}
    
    \begin{shaded}
      { \fangsong\color{white} Cowards die many times before their deaths.\\
        懦夫在未死之前，已身历多次死亡的恐怖了。（仿宋）}\\
    \end{shaded}

   { \lishu 夏天的飞鸟，飞到我的窗前唱歌，又飞去了。\\
        秋天的黄叶，它们没有什么可唱，只叹息一声，飞落在那里。（隶属）}\\
    \hfill \emph{罗宾德拉纳特·泰戈尔}

    \mybox{red!70!black}{例2.8\;电路及元件参数如图所示：}
    {
         懦夫在未死之前，已身历多次死亡的恐怖了。
    }

    \mybox{teal}{例2.8\;电路及元件参数如图所示：}
    {
         \youyuan 懦夫在未死之前，已身历多次死亡的恐怖了。（幼圆）
    }

    \mybox{green!70!black}{Super Mega Ultra Long Fancy Title}
    {
        \begin{enumerate}
            \item Show that\\
            $\displaystyle D_2f(x,y) = \frac{\partial {}}{\partial{y}} \biggl( \int_0^xg_1 (t,0) \ dt + \int_0^y g_2(x,s) \ ds \biggr)$
            \item prove that\\
            $\displaystyle \biggl(\forall x\in\mathbb{R}  \biggr)\biggl(\forall y \in \mathbb{R} \biggr) x\neq y\, \text{ and } \, x+y \neq 2 \implies x^{2}-2x \neq y^2-2y$
        \end{enumerate}
    }

    夏天的飞鸟，飞到我的窗前唱歌，又飞去了。\\
    秋天的黄叶，它们没有什么可唱，只叹息一声，飞落在那里。\\
    \hfill \emph{罗宾德拉纳特·泰戈尔}
\end{document}